---
title: "EBICGlasso Analyses"
output: html_notebook
---

---
title: "EBICGlasso Analyses"
output: html_notebook
---

NOTE: This script is only provided to demonstrate how EBICGlasso was implemented in this study. The response data collected in this study is NOT made publicly available to protect the identities of the participants.

```{r}
library(tidyverse)
library(qgraph)
library(psych)
set.seed(2020)

all_items_w_prompts = openxlsx::read.xlsx("/Users/Alex/Library/Mobile Documents/com~apple~CloudDocs/School/Dissertation/Defense/Results/HEXACO Item-Facet Key 8-20.xlsx")

#df = openxlsx::read.xlsx("/Users/Alex/Library/Mobile Documents/com~apple~CloudDocs/School/Dissertation/Defense/Data/MTurk Pilot/Cleaned Response Data No Attn.xlsx") 
df = openxlsx::read.xlsx("/Users/Alex/Library/Mobile Documents/com~apple~CloudDocs/School/Dissertation/Analyses/Cleaned Response Data No Attn.xlsx") 
dim(df)

item_info = openxlsx::read.xlsx("/Users/Alex/Library/Mobile Documents/com~apple~CloudDocs/School/Dissertation/Analyses/Item_Info.xlsx")
```

Build df for Item Info and HEXACO Facets used for generation
```{r}
item_info = item_info %>% 
  select(contains(c("Agreeableness", "Conscientiousness", "Emotionality", "Extraversion", "Openness", "Honesty.Humility"))) %>% 
  t(.) %>% as.data.frame(.)

colnames(item_info) = "Item"

#hexaco_facets = hexaco_facets %>% 
all_items_w_prompts = all_items_w_prompts %>% 
  select(Item, contains(c("Factor","Facet","Prompt_")))

item_info = item_info %>%
  mutate(Idx = rownames(.)) %>% 
#  full_join(., hexaco_facets)
  left_join(., all_items_w_prompts)

```


```{r}
lvls = c("Very Inaccurate", "Moderately Inaccurate", "Neither Accurate Nor Inaccurate", "Moderately Accurate", "Very Accurate")
lbls = c(1:5)

net_df = df   %>% 
#  filter( !grepl(x = Agreeableness_1, pattern = "In general,|ImportId")) %>% 
  dplyr::select(contains( c("Agreeableness","Conscientiousness", "Emotionality", "Openness", "Extraversion", "Honesty.Humility") )) #%>% 
#           map(.x = ., .f = ~factor(.x, levels = lvls, labels = lbls)) %>% 
#         map(.x = ., .f = ~as.numeric(.x)) %>% bind_cols(.) 

```


# Totals 
Address reverse coded items!!!!
```{r}
factor_totals = pmap(.l = list(factor = c("Agreeableness","Conscientiousness", "Emotionality", "Openness", "Extraversion", "Honesty.Humility")),
     .f = function(factor){
       factor <- enquo(factor)
        net_df %>% 
         dplyr::select(contains(!!factor)) %>% 
         mutate(!!factor := rowSums(.)) %>% 
         dplyr::select(!!factor)
     }) %>% 
  bind_cols(.)

cor(factor_totals)
```

```{r}
pwalk(.l = list(df_name = c("ag","co", "emo", "ext", "opn", "hh"), factor_name = c("Agreeableness","Conscientiousness", "Emotionality", "Extraversion", "Openness", "Honesty.Humility")), net_df,
 .f = function(df_name, factor_name, net_df){
   curr_df <- net_df %>% 
     dplyr::select(matches(factor_name))
   
   assign(x = df_name, value = {{curr_df}}, envir = globalenv() )
 }
 )
```

```{r}
results <- bootnet::estimateNetwork(
      ag,
      default = 'EBICglasso',
      corMethod = 'cor_auto',
 #     corMethod = 'spearman',
      threshold = F,
      nlambda = 60,
      tuning = 0,
      
      #criterion = "ebic",
      penalize.diagonal = T,
    sampleSize = "minimum",
    # refit = F,
    countDiagonal = T,
    verbose=T
    
  )


best_lambda <- results$results$results$rholist[which.min(results$results$ebic)]
best_ebic <- results$results$ebic[which.min(results$results$ebic)]
best_lambda ;best_ebic
```



Functions for generating results.
```{r}
# Runs qgraph::EBICglasso() for one gamma value and num_lambda lambda values
run_EBICglasso <- function(.dat, .gamma, num_lambda = 30){
  
  results <- bootnet::estimateNetwork(
      data = .dat,
      default = 'EBICglasso',
      corMethod = 'cor_auto',
 #     corMethod = 'spearman',
      threshold = F,
      nlambda = num_lambda,
      tuning = .gamma,
      
      #criterion = "ebic",
      penalize.diagonal = F,
    sampleSize = "minimum",
    # refit = F,
    countDiagonal = F,
    verbose=T
  )
    
    # Log the EBIC values, their respective lambda values, and their rank (w.r.t. EBIC).
    params = cbind.data.frame(1:num_lambda, results$results$ebic, results$results$lambda, Gamma = .gamma); colnames(params) = c("IDX","EBIC", "Lambda", "Gamma")
    ebic_rank = params %>% arrange(EBIC) %>% mutate(EBIC_Rank = 1:nrow(params)) %>% select(EBIC, EBIC_Rank) 
    params = left_join(params, ebic_rank)
    
    # Return a list containing the run log, and all partial correlation networks
    run_list = list(params, results$results$results$w)
    #run_list = list(params, results)#$results$w)
    
    
    return(run_list)
}

# Map the above function across a range of gamma values (gamma_string), for a given dataset (.dat).
map_EBICglasso = function(.dat, gamma_string = c(0, .25, .5))    mapped_results = map(.x = gamma_string, .f = ~run_EBICglasso(.dat = {{.dat}}, .gamma = .x))


```
Get all results
```{r}
ag_results = map_EBICglasso(ag)
co_results = map_EBICglasso(co)
emo_results = map_EBICglasso(emo)
ext_results = map_EBICglasso(ext)
opn_results = map_EBICglasso(opn)
hh_results = map_EBICglasso(hh)
```


```{r}
ag_results[[1]][[1]]; ag_results[[2]][[1]];ag_results[[3]][[1]]
```

```{r}

iter_plot = function(.results, i, .layout = "spring", label_scale = 1, node_labels = c(), legend_label_scale = .3, layout_ratio = 1.85, edge_labels = F){
  curr_net = .results[[1]][[2]][1:16, 1:16, i]
  
  curr_Lambda = round(.results[[1]][[1]]$Lambda[i], digits = 3)
  lambda_expression = substitute(lambda[i] == curr_Lambda, list(i = i, curr_Lambda = curr_Lambda))
  
  g1 = round(.results[[1]][[1]]$EBIC[i], digits = 0)
  g2 = round(.results[[2]][[1]]$EBIC[i], digits = 0)
  g3 = round(.results[[3]][[1]]$EBIC[i], digits = 0)
  
  g1_expression = substitute(gamma[1] == g1, list(g1 = g1))
  g2_expression = substitute(gamma[2] == g2, list(g2 = g2))
  g3_expression = substitute(gamma[3] == g3, list(g3 = g3))
  lambda_lbl = c(
    lambda_expression, 
    g1_expression, 
    g2_expression, 
    g3_expression, 
    expression() # Leaving this at the end of the string forces all other items prior to be evaluated as an expression! No idea why but great!!!
                 
#                 expression(gamma[0] == phantom(0)), bquote(.(round(.results[[1]][[1]]$EBIC[i], digits = 0))),
#                 expression(gamma[.25] == phantom(0)), bquote(.(round(.results[[2]][[1]]$EBIC[i], digits = 0))),
#                 expression(gamma[.5] == phantom(0)), bquote(.(round(.results[[3]][[1]]$EBIC[i], digits = 0)))
                 
                 )
  
  if(length(node_labels) > 0){ 
  plt = qgraph::qgraph(input = curr_net, layout = .layout, threshold = "sig", sampleSize = 292, normalize = F, DoNotPlot = F, 
   nodeNames = node_labels, legend.cex = legend_label_scale, GLratio = layout_ratio,
   edge.labels = edge_labels);
  
  text(c(-1),# X-axis plotting locations for LHS and RHS of hyperparameter-value pairs.
       c(1.2,1.05,.9,.75), labels = lambda_lbl, cex = label_scale ) # Y-axis plotting locations for LHS and RHS of hyperparameter-value pairs.

  }else{
    plt = qgraph::qgraph(input = curr_net, layout = .layout, threshold = "sig", sampleSize = 292, normalize = F, DoNotPlot = F,  edge.labels = edge_labels);
  text(c(-1),# X-axis plotting locations for LHS and RHS of hyperparameter-value pairs.
       c(1.2,1.05,.9,.75), labels = lambda_lbl, cex = label_scale ) # Y-axis plotting locations for LHS and RHS of hyperparameter-value pairs.
  
  }
  return(plt)
}



```



```{r}
save_nets <- function(.results, file_name = file_name){

  plt_idx <- 1:30
  best_idxs = list()
  best_idxs[[1]] = which(.results[[1]][[1]]$EBIC_Rank == 1)
  best_idxs[[2]] = which(.results[[2]][[1]]$EBIC_Rank == 1)
  best_idxs[[3]] = which(.results[[3]][[1]]$EBIC_Rank == 1)

  png(file_name, width = 3000, height = 3000)


  layout(matrix(c(1,1,2,3,4,5,6, 1,1,7,8,9,10,11, 12,13,14,15,16,17,18,
                19,20,21,22,23,24,25, 26,27,28,29,30,31,32), 5, 7, byrow = T), respect = T);
  iter_plot(.results = {{.results}}, i =  best_idxs[[3]], .layout = "circle", label_scale = 4)
  
  walk(.x = plt_idx, .results = {{.results}}, best_idx = unlist(best_idxs), 
       .f = function(.x, .results, best_idx){ 
    iter_plot(.results = .results, i = .x, .layout = "circle", label_scale = 2);
    if(.x == best_idx[1]) polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", lwd = 5, border = "red") # Outline Plot if current idx matches best_idx
    if(.x == best_idx[2]) polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", lwd = 5, border = "#FFCC00") # Outline Plot if current idx matches best_idx
    if(.x == best_idx[3]) polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", lwd = 5, border = "green") # Outline Plot if current idx matches best_idx
    })

  dev.off()
}
#ag_results[[1]][[2]][1:16,1:16,1]
```

Generate plots containing all 30 networks for each of the 6 factors.
```{r}
save_nets(.results = ag_results, file_name = "Agreeableness_Nets.png")
save_nets(.results = co_results, file_name = "Conscientiousness_Nets.png")
save_nets(.results = emo_results, file_name = "Emotionality_Nets.png")
save_nets(.results = ext_results, file_name = "Extraversion_Nets.png")
save_nets(.results = opn_results, file_name = "Openness_Nets.png")
save_nets(.results = hh_results, file_name = "Honesty-Humility_Nets.png")

```

```{r}
centralities <- qgraph::centrality_auto(ag_results[[1]][[2]][1:16,1:16,3], signed = T)
clusters <- qgraph::clustcoef_auto(ag_results[[1]][[2]][1:16,1:16,3])
centralities; clusters
```




```{r}
node_dat <- cbind.data.frame(centralities$node.centrality$Strength, centralities$node.centrality$Betweenness, clusters$signed_clustZhang)
colnames(node_dat) <- c("Strength", "Betweenness", "Signed_Zhang")

ggplot(data = node_dat, aes(x = Strength, y = Signed_Zhang, Betweenness)) +
  ggplot2::geom_point(size = 2, mapping = aes(color = Betweenness)) +
 theme(axis.text.x = element_text(), axis.line = element_line()) +
  #coord_cartesian(xlim = c(.0075,.015), ylim = c(.07,.2)) + 
  geom_label(mapping = aes(label = rownames(node_dat), color = Betweenness)) +
   scale_color_gradient2(low = "yellow", mid = "darkblue", high = "red", midpoint = mean(node_dat$Betweenness))
```

#### Evaluating the Best Performing, Most Parsimonious Partial Correlation Networks
Plots 3 Networks for a Given Factor...
```{r}
best_nets <- function(.results, indices, save_plot = F, ...){

  factor_name = NULL # for adding items to legend...
  label_scale = 1
  legend_label_scale = .5 # Will need to increase when exporting!
  legend_y = 6 # Might need to tweak...
  legend_x = 3 # Should be centered every time...
  title_scale = 1
  
  
  
  elements = rlang::dots_list(..., .named = T)
  pwalk(.l = list(var = names(elements), val = elements),  .f = function(var, val) assign(x = var, value = val, envir = sys.frame(-3) )) 
  
if(!is.null(factor_name)){  
  # Get item text
  node_labs = item_info %>%
    filter(grepl(x = Idx, pattern = factor_name)) %>% 
    select(Item) %>% 
    unite(Facet) %>% 
    select(Facet) %>% 
    unlist(., use.names = F)
  
  # Find best spot to add '\n' for longer items...
  idx = imap(
  .x = node_labs,
  .f = function(x, .id ){
   str_locate_all(string = node_labs[.id], pattern = " ") %>%
      as.data.frame(.) %>% cbind.data.frame(.,  .[,1] > 25) %>% filter(.[,3]) %>% 
      select(start) %>% unlist(., use.names = F)  %>% .[1]
    }) %>%
    unlist(., use.names = F) 
 
  # Update longer items to split using idx...
node_labs <-   pmap_chr(.l = list(label = node_labs, idx = idx), .f = function(label, idx){
    if(!is.na(idx)){ 
      substr(x = label, start = idx, stop = idx) <-  '\n'; label 
    }else{paste0(label, "\n")}  }) 

node_labs <- str_glue('{idx}. {lab}{sep}', lab = node_labs, sep = rep(c('\n','\n','\n','NEXT BLOCK'), times = 4), idx = 1:16)
node_labs  <-  glue::glue_collapse(node_labs) %>% str_split(string = ., pattern = "NEXT BLOCK") %>% unlist(., use.names = F)
node_labs <- node_labs[-5] # Might not always have an empty last string??? WHY IS IT THERE???

}else{node_labs = NULL}
  
if(save_plot){
  file_name = paste0("Best_", factor_name, "_Nets",".png")
  png(file_name, width = 3000, height = 1500)
  
}  

layout(mat = matrix(c(1,2,3), nrow = 1, byrow = T), respect = T);

pmap(.l = list(curr_idx = indices, curr_col = c("red", "yellow", "green")), .f = function(curr_idx, curr_col){
  
iter_plot(.results = .results, i = curr_idx, .layout = "spring", label_scale = label_scale, edge_labels = F); 
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = curr_col, lwd = 4)  
});
  
if(!is.null(node_labs)){
  
  block_shift_y = map_dbl(.x = node_labs, .f = function(x) x %>% str_count(string = ., pattern = "\n") %>% sum(.)) + legend_y
  #block_shift_x = c(-.8,-.55,-.3,-.05)*legend_x
  block_shift_x = (seq(-.75,1,by=.5)*legend_x)-3
  
  pwalk(.l = list(lab = node_labs, block_y = block_shift_y, block_x = block_shift_x), .f = function(lab, block_x, block_y){
  mtext(text = lab, side = 1, outer = F, cex = legend_label_scale, adj = 0, lheight = 0,
      #at = c(-6.5,-4.5,-2.5,-0.5), line = c(6,8,10,12)
      at = block_x, line = block_y
      )
  })
};

if(!is.null(factor_name)) mtext(text = factor_name, side = 3, line = 5, at = -2.5, cex = 2*title_scale, adj = .5, padj = 0)

if(save_plot) dev.off()
}

```


```{r}
best_nets(.results = ag_results, factor_name = "Agreeableness", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)
best_nets(.results = ag_results, factor_name = "Agreeableness", indices = c(12,16,19), 
           legend_label_scale = .5, legend_y = 6, title_scale = 1)


best_nets(.results = emo_results, factor_name = "Emotionality", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)
best_nets(.results = co_results, factor_name = "Conscientiousness", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)
best_nets(.results = ext_results, factor_name = "Extraversion", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)
best_nets(.results = opn_results, factor_name = "Openness", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)
best_nets(.results = hh_results, factor_name = "Honesty.Humility", indices = c(12,16,19), 
          label_scale = 2, legend_label_scale = 1.5, legend_y = 16, title_scale = 2, save_plot = T)

```


```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Agreeableness")) %>% 
  #select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(ag_results, 19, .layout = "spring", label_scale = 1, node_labels = node_labs, edge_labels = F, legend_label_scale = .5); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```

```{r}
graph_mat <- qgraph(ag_results[[3]][[2]][1:16,1:16,19])
qgraph::smallworldIndex(x = graph_mat)

centralities <- qgraph::centrality_auto(x = graph_mat, signed = T)
centralities$node.centrality
qgraph::clustcoef_auto(x = graph_mat)

edge_dat = cbind.data.frame(graph_mat$Edgelist$from, graph_mat$Edgelist$to, graph_mat$Edgelist$weight) 
colnames(edge_dat) = c("from", "to", "weight")  
#edge_dat %>% 
#  filter(from == 5 | to == 5)

item_info %>% filter(grepl(Idx, pattern = "Agreeableness")) %>% 
  select(Item, Idx, contains(c("Facet", "Prompt"))) 

#item_info %>% filter(grepl(Idx, pattern = "Emotionality")) %>% 
#  select(contains("Prompt")) %>% 
#  unlist(., use.names = F) %>% 
#  cbind.data.frame(.) %>% 
#  table(.)
```


```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Conscientiousness")) %>% 
#  select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(co_results, 21, .layout = "spring", label_scale = 1, node_labels = node_labs, legend_label_scale = .275, layout_ratio = 1.7, edge_labels = F); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```


```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Emotionality")) %>% 
#  select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(emo_results, 20, .layout = "spring", label_scale = 1, node_labels = node_labs, legend_label_scale = .275, layout_ratio = 1.7); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```

```{r}
graph_mat <- qgraph(emo_results[[3]][[2]][1:16,1:16,20])
qgraph::smallworldIndex(x = graph_mat)

centralities <- qgraph::centrality_auto(x = graph_mat, signed = T)
centralities$node.centrality
qgraph::clustcoef_auto(x = graph_mat)

edge_dat = cbind.data.frame(graph_mat$Edgelist$from, graph_mat$Edgelist$to, graph_mat$Edgelist$weight) 
colnames(edge_dat) = c("from", "to", "weight")  
#edge_dat %>% 
#  filter(from == 5 | to == 5)

item_info %>% filter(grepl(Idx, pattern = "Emotionality")) %>% 
  select(Item, Idx, contains(c("Facet", "Prompt"))) 

#item_info %>% filter(grepl(Idx, pattern = "Emotionality")) %>% 
#  select(contains("Prompt")) %>% 
#  unlist(., use.names = F) %>% 
#  cbind.data.frame(.) %>% 
#  table(.)
```



```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Extraversion")) %>% 
 # select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(ext_results, 19, .layout = "spring", label_scale = 1, node_labels = node_labs, legend_label_scale = .28, layout_ratio = 2.2); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```

```{r}
graph_mat <- qgraph(ext_results[[3]][[2]][1:16,1:16,19])
qgraph::smallworldIndex(x = graph_mat)

qgraph::centrality_auto(x = graph_mat, signed = T)
qgraph::clustcoef_auto(x = graph_mat,.1)

edge_dat = cbind.data.frame(graph_mat$Edgelist$from, graph_mat$Edgelist$to, graph_mat$Edgelist$weight) 
colnames(edge_dat) = c("from", "to", "weight")  
edge_dat %>% 
  filter(from == 5 | to == 5)
```


```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Openness")) %>% 
#  select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(opn_results, 20, .layout = "spring", label_scale = 1, node_labels = node_labs, legend_label_scale = .275, layout_ratio = 1.7); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```

```{r}
node_labs = item_info %>%
  filter(grepl(x = Idx, pattern = "Honesty.Humility")) %>% 
  #select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(hh_results, 20, .layout = "spring", label_scale = 1, node_labels = node_labs, legend_label_scale = .275, layout_ratio = 1.7); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green")  
```

```{r}
hh_results[[1]][[2]][1:16, 1:16, 20]
```

#### FULL NET??


```{r}
# Drop redundant/poor fitting items to get cov_mat for net_df that is positive-definite?
net_df2 = net_df %>% select(!Conscientiousness_5) %>% select(!contains("Honesty.Humility")) %>% select(!contains("Agreeableness"))
full_net = map_EBICglasso(net_df2)

#(95*96)/2
#partial.r(net_df2) %>% lower.tri(.) %>%  sum(.)
```
```{r}
node_labs = item_info %>%
  filter(Idx %in% colnames(net_df2)) %>% 
  #select(contains("Facet")) %>% 
  select(Item) %>% 
  unite(Facet) %>% 
  select(Facet) %>% 
  unlist(., use.names = F)

iter_plot(full_net, 25, .layout = "spring", label_scale = 1, node_labels = node_labs, edge_labels = F); # Example Plot
    polygon(c(-1.25, -1.25, 1.25, 1.25), c(-1.25, 1.275, 1.275, -1.25), col= "transparent", border = "green") 
```
